\cvsection{Experience}

\cvevent{Senior Data Scientist}{DHL}{Bonn}{Feb 2025 -- Present}


\cvevent{Senior Data Scientist}{Bain}{Düsseldorf}{Nov 2021 -- Jan 2025}
\begin{itemize}
    \item Leading the development and implementation of unsupervised learning products and GenAI for various industries.
    \item Prototyped, developed, and deployed production-ready (on Azure) GenAI solutions to enhance banking operations, specializing in customer service and financial analysis.
    \item Developed a high-performing multi-modal mixture model capable of segmenting mixed data from customer surveys. The model achieved a 6\% improvement over the Scikit-Learn GMM benchmark.
\end{itemize}

\cvevent{Data Scientist}{E.ON SE}{Essen}{Jan 2020 -- Oct 2021}
\begin{itemize}
    \item Led the development of a variational autoencoder (VAE) model as part of
EON’s global predictive maintenance strategy. This innovative model enabled a 20\% increase in lead time for preventive maintenance on high voltage transformers, saving the company millions in potential downtime costs.  
    \item co-designed and deployed a multi-objective optimization framework for integrating small-scale electric vehicle (EV) charging infrastructure into distributed systems. This framework leverages Model Predictive Control (MPC) for a smart charging strategy that optimizes both grid stability and charging efficiency.

\end{itemize}

\cvevent{Research Assistant}{Fraunhofer ISE}{Freiburg}{May 2017 -- Mar 2019}
\begin{itemize}
    \item Developed numerous simulation models for distributed generation systems, incorporating various uncertainties, as a key component of my research thesis.
\end{itemize}